ZCB Pricing

### 2018-08-06 ZCB Pricing .Rmd
modified sensitivity graphics

  for (i in 1:(length(I)-1)){
    C_2 <- matrix(0,nrow = M,ncol = 1)
    C_2[1,1] <- pd(1)*Bond_values_2[1,1]
    C_2[M,1] <- pu(M)*Bond_values_2[1,1]

@@

    RHS <- Diag_2%*%Bond_values_1 + C_1 + C_1
    Bond_values <- Inv%*%RHS
    Bond_values_2 <- Bond_values_1
    Bond_values_1 <- Bond_values
  }

@@

senses <- matrix(nrow=13, ncol=9) # matrix to hold prices for various parameters
colnames(senses) <-c("Parameters","Closed Form","Crude Monte Carlo","Antithetic Variates","Moment Matching","Control Variates","Explicit","Implicit","Crank-Nicholson")
#xvec=c(Closed Form,Crude Monte Carlo,Antithetic Variates,Moment Matching,Control Variates,Explicit,Implicit,Crank Nicholson) #list of numerical methods

@@

par(mfrow=c(1,1))
plot(x=1:8,y=senses[1,2:9], ylim =c(0.58,0.66), xlab = "Numerical Method", ylab = "Bond Price", main = "Sensitivity Test: Interest Rate")
#axis(1, at=1:8, labels=xvec)
lines(1:8, senses[2,2:9], col="red",type = "p")
lines(1:8, senses[3,2:9],col ="blue",type = "p")
legend("bottomright", inset = c(-0,0), legend = c("r=0.05", "r=0.08", "r=0.1"), lty = c(1,1,1), col = c("red","black","blue", "red"), cex = 0.8, bty ="n")

@@

time_vec <- seq(0,100,1)

@@

par(mfrow = c(1,1))
plot(closed, x = time_vec, type = "l", ylim = c(0.53,0.65), xlab = "Number of time steps", ylab = "Estimated Price" , lty =1, font.main = 1, main = "Finite Difference Bond Prices as Time Steps Increase")
lines(x = time_vec, y = CN_conv, type = "l", lty = 2, lwd =1.5)
lines(x = time_vec, y = Impl_conv, type = "l", lty = 2, col = "blue",lwd =1.5)
lines(x = time_vec, y = Expl_conv, type = "l", lty = 2, col = "red",lwd =1.5)
legend(x = 60, y = 0.6, legend = c("Closed Form", "Crank-Nicolson", "Implicit", "Explicit"), lty = c(1,2,2,2), col = c("black","black","blue", "red"), cex = 0.8, bty ="n")

>>>>

  for (i in 1:(length(I)-1)){
    C_2 <- matrix(0,nrow = M,ncol = 1)
    C_2[1,1] <- pd(1)*Bond_values_2[1,1]
    C_2[M,1] <- pu(M)*Bond_values_2[M,1]

@@

    RHS <- Diag_2%*%Bond_values_1 + C_1 + C_2
    Bond_values <- Inv%*%RHS
    Bond_values_2 <- Bond_values_1
    Bond_values_1 <- Bond_values
  }

@@

senses <- matrix(nrow=13, ncol=9) # matrix to hold prices for various parameters
colnames(senses) <-c("Parameters","Closed Form","Crude Monte Carlo","Antithetic Variates","Moment Matching","Control Variates","Explicit","Implicit","Crank-Nicholson")
xvec=c("Closed Form","Crude","AV","MM","CV","Explicit","Implicit","CN") #list of numerical methods

@@

par(mfrow=c(1,1))
plot(x=1:8,y=senses[1,2:9], ylim =c(0.58,0.66), xlab = "Numerical Method", ylab = "Bond Price", main = "Sensitivity Test: Interest Rate", xaxt = "n", col ="black", pch = 19, font.main = 1)
axis(1, at=1:8, labels=xvec)
lines(1:8, senses[2,2:9], col="red",type = "p", pch = 19)
lines(1:8, senses[3,2:9],col ="blue",type = "p", pch =19)
legend("bottomright", inset = c(-0,0), legend = c("r = 0.05", "r = 0.08", "r = 0.10"), lty = c(1,1,1), col = c("red","black","blue", "red"), cex = 0.8, bty ="n", pch =19)

@@

time_vec <- seq(1,100,1)

@@

par(mfrow = c(1,1))
plot(closed, x = time_vec, type = "l", ylim = c(0.59,0.65), xlab = "Number of time steps", ylab = "Estimated Price" , lty =1, font.main = 1, main = "Finite Difference Bond Prices as Time Steps Increase")
lines(x = time_vec, y = CN_conv, type = "l", lty = 2, lwd =1.5, col = "green")
lines(x = time_vec, y = Impl_conv, type = "l", lty = 2, col = "blue",lwd =1.5)
lines(x = time_vec, y = Expl_conv, type = "l", lty = 2, col = "red",lwd =1.5)
legend(x = 60, y = 0.62, legend = c("Closed Form", "Crank-Nicolson", "Implicit", "Explicit"), lty = c(1,2,2,2), col = c("black","green","blue", "red"), cex = 0.8, bty ="n")
